\Title

### 2020-11-10 manuscript/manuscript.tex
Specify gravity constant

\noindent where $z_i$ and $z_j$ are the vertical components of the
$\mathbf{p}_i$ and $\mathbf{q}_j$ points, respectively.

>>>>

\noindent where
$G = \SI{6.674e-11}{\cubic\meter\per\kilogram\per\second\squared}$ is the
universal gravitational constant, $z_i$ and $z_j$ are the vertical components
of the $\mathbf{p}_i$ and $\mathbf{q}_j$ points, respectively.
